\section{Introduction}

Cloud computing enables its subscribers to use computing services over the 
Internet and provides tailored computing resources on-demand. 
Subscribers of cloud storage often outsource their data on public cloud servers
to ensure that it is highly available and reliabile~\cite{wang2012toward}. 
It is then the cloud service provider's
responsibility to coordinate data backup, synchronization and sharing
with relevant stakeholders. 

As the amount of data stored on the cloud increases dramatically, the security 
of this data has become an important concern. Recent cases~\cite{top_threats}
have included users' photos and videos getting stolen from compromised cloud servers resulting in
severe breaches of privacy. Credit card numbers and medical
records are other examples of user data whose privacy needs to be ensured.

The straightforward way to achieve data protection and confidentiality is to
place data on the cloud after encrypting it using public key encryption.
This solves the confidentiality and privacy problem
but encryption hides information within the data and searching becomes difficult. The user
has to download all of the data from cloud storage and search it after decrypting it locally. This is
obviously an extremely expensive proposition. Therefore we need a mechanism 
which can enable a user to search over the encrypted data without revealing 
private information and without downloading excessive data over the network.

Existing approaches for searching over encrypted data often rely on
``trapdoors"~\cite{song,goh2003secure,boneh}. 
Trapdoors enable a user to search the encrypted data for a small 
set of pre-defined keywords. These approaches restrict the searching
capability of a user to a limited number of trapdoors defined during data 
encryption. More recent work has focused on homomorphic encryption~\cite{craig,zeehan} as a solution
to this problem. However, to ensure privacy from the cloud service provider (CSP), 
all the evaluated results
are returned from the cloud server in encrypted form without any compression. This causes high data
communication cost but naively allows searching for exact keyword matches over the encrypted data.

In this paper, we present a novel system for performing searches on encrypted 
data in the cloud. We propose a novel compression technique which allows us to
avoid sending back the entire encrypted index back to the client. This reduces the cost of
communicating search results back to the client by over 95\% resulting in 
faster response times and less budgeting cost (\$) to the owner. 
In addition to exact keyword matching, our system also
supports similarity-based searching: finding documents with partially matching 
keywords rather than only those with exactly matching ones. Privacy and search 
capabilities are enabled using homomorphic encryption, while sliding window 
bloom filters allow us to search for partially matching keywords. 

The rest of the paper is organized as follows. The next section overviews
related work in more detail.
Section \ref{sec:system} presents a detailed description of our system and the 
algorithms it uses.
Section \ref{sec:eval} demonstrates the benefits of using our approaches
on a dataset of encrypted textual data. Finally, sections \ref{sec:futurework} and 
\ref{sec:conclusion} conclude with a treatment of some limitations and trade-offs of our system.
